Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Better labelling of timeout and oom.
Macrofied the change? boolean.

\begin{itemize}
 \item{{\tt $\msto$}, the store}
 \item{{\tt todo}, the workset}
 \item{{\tt seen}, a map from states to the timestamps at which they were last seen}
 \item{{\tt $\msdiff$}, the store changes for the current step}
 \item{{\tt $\msdiff$?}, a boolean tracking whether the stepped state contributed a store change}
 \item{{\tt T}, the timestamp of the store}
\end{itemize}

The new $eval$ calculation is defined in
figure~\ref{fig:imperative}.  To ensure termination, we guard adding
$c$ to {\tt todo} by the following check:
\begin{align*}\msdiff\mbox{{\tt ?}} \vee {\tt seen}(c) \neq {\tt T}\end{align*}
If it succeeds, {\tt todo} gets $c$ and we update {\tt seen} to map $c$ to {\tt T}.

After all steps complete, we apply $\msdiff$ to $\msto$ imperatively
(with {\tt replay!}) and increase {\tt T} as long as there was at
least one change in $\msdiff$. This logic leads to termination if we
know that each $\ttuple{\maddr}{\mval{s}}$ in $\msdiff$ would change
the value of $\maddr$ in the current store. Thus, we also guard
additions to $\msdiff$ so that only updates that would change the
store are permitted. Each time $\msdiff$ is successfully extended, we
set {\tt $\msdiff$?} to true. Before each individual step, we set it
to false.

\begin{figure}
\begin{alltt}
eval(\(e\)) :=
  \(\msto\), todo, seen, T := \(\varnothing\), \(\varnothing\), [], 0
  \(\compile{e}\)(\(\mtcntr, \varnothing, \varnothing, \kmt\))
  while(true):
    if todo = \(\varnothing\): return (keys(seen), \(\msto\))
    else:
      let old := todo
      todo, \(\msdiff\) := \(\varnothing\), \(\mtlst\)
      foreach c \(\in\) old: \(\msdiff\)? := false; c()
      unless \(\msdiff\) = \(\mtlst\): T += 1; replay!(\(\msdiff, \msto\))
\end{alltt}
\caption{Imperative algorithm}
\label{fig:imperative}
\end{figure}

@@

\begin{figure}
\include{bench-overview}
\caption{Overview performance comparison between baseline and
  optimized analyzer.}
\label{fig:bench-overview}
\end{figure}

>>>>

\begin{itemize}
 \item{$\msto$, the store}
 \item{{\tt todo}, the workset}
 \item{{\tt seen}, a map from states to the timestamps at which they were last seen}
 \item{$\msdiff$, the store changes for the current step}
 \item{$\changep$, a boolean tracking whether the stepped state contributed a store change}
 \item{{\tt T}, the timestamp of the store}
\end{itemize}

The new $eval$ calculation is defined in
figure~\ref{fig:imperative}.  To ensure termination, we guard adding
$c$ to {\tt todo} by the following check:
\begin{align*}\changep \vee {\tt seen}(c) \neq {\tt T}\end{align*}
If it succeeds, {\tt todo} gets $c$ and we update {\tt seen} to map $c$ to {\tt T}.

After all steps complete, we apply $\msdiff$ to $\msto$ imperatively
(with {\tt replay!}) and increase {\tt T} as long as there was at
least one change in $\msdiff$. This logic leads to termination if we
know that each $\ttuple{\maddr}{\mval{s}}$ in $\msdiff$ would change
the value of $\maddr$ in the current store. Thus, we also guard
additions to $\msdiff$ so that only updates that would change the
store are permitted. Each time $\msdiff$ is successfully extended, we
set $\changep$ to true. Before each individual step, we set it
to false.

\begin{figure}
\begin{alltt}
eval(\(e\)) :=
  \(\msto\), todo, seen, T := \(\varnothing\), \(\varnothing\), [], 0
  \(\compile{e}\)(\(\mtcntr, \varnothing, \varnothing, \kmt\))
  while(true):
    if todo = \(\varnothing\): return (keys(seen), \(\msto\))
    else:
      let old := todo
      todo, \(\msdiff\) := \(\varnothing\), \(\mtlst\)
      foreach c \(\in\) old: \(\changep\) := false; c()
      unless \(\msdiff\) = \(\mtlst\): T += 1; replay!(\(\msdiff, \msto\))
\end{alltt}
\caption{Imperative algorithm}
\label{fig:imperative}
\end{figure}

@@

\begin{figure}
\include{bench-overview}
\caption{Overview performance comparison between baseline and
  optimized analyzer (entries of \text{{\small $t$}} mean timeout, and \text{{\small $m$}} mean out of memory).}
\label{fig:bench-overview}
\end{figure}
